Safe Transferable Regions

### 2017-01-11 paper/related.tex
ownwership inference related work

Our region type system can also be thought of as a specialized
ownership type system~\cite{OwnershipSurvey}, where each region is the
owner of all objects allocated in the region.
%
An ownership type system for safe region-based memory management in
real-time Java has been proposed by~\cite{MIT03}.  
% Like us, they too assume a source language with programmer-managed
% memory regions, and focus on proving safety of programs written in
% that language.  
Their language permits only lexically-scoped (stack) regions.
% (in the context of shared-memory concurrency).
In contrast, we permit regions with dynamically determined lifetimes.
% (in the context of message-passing concurrency).
% We borrow outlives relation from their formal
% development, and our type system bears some similarities to theirs.
Our language also admits generics and higher-order functions.
We also establish type safety and transfer safety results that
formalize the guarantees provided by our system. While~\cite{MIT03}'s
language is explicitly typed, our language comes equipped with full
type inference.

% Although there is some support for local
% type inference, region types for methods and classes need to be
% written explicitly. In contrast, our region type inference that
% eliminates any such need.
% Our type inference algorithm is also novel compared to existing type
% inference approaches for ownership types, which are based on, e.g.,
% context-insensitive pointer analysis or boolean satisfiability.
% E.g., papers 55 and 79.

>>>>

Our region type system can also be thought of as a specialized
ownership type system~\cite{OwnershipSurvey}, where each region is the
owner of all objects allocated in the region.
%
An ownership type system for safe region-based memory management in
real-time Java has been proposed by~\cite{MIT03}.  
% Like us, they too assume a source language with programmer-managed
% memory regions, and focus on proving safety of programs written in
% that language.  
Their language permits only lexically-scoped (stack) regions.
% (in the context of shared-memory concurrency).
In contrast, we permit regions with dynamically determined lifetimes.
% (in the context of message-passing concurrency).
% We borrow outlives relation from their formal
% development, and our type system bears some similarities to theirs.
Our language also admits generics and higher-order functions.
We also establish type safety and transfer safety results that
formalize the guarantees provided by our system. While~\cite{MIT03}'s
language is explicitly typed, our language comes equipped with full
type inference.
However, several inference algorithms have been proposed in the context
of other ownership type systems.
Our type inference algorithm is also novel compared to these existing
ownership inference algorithms, which are based on, e.g.,
pointer analysis~\cite{HuangEtAl:ECOOP12} or boolean satisfiability~\cite{DietlEtAl:ECOOP11}.
(See Section 5.2 of~\cite{OwnershipSurvey} for a more comprehensive discussion
of ownership inference algorithms.)
Some distinguishing characteristics of our algorithm is that it is customized
to our problem, does not use any pointer analysis algorithm (which
can be a source of imprecision) or SAT solvers (which can be a source of inefficiency),
and comes with relative completeness guarantees.

% Although there is some support for local
% type inference, region types for methods and classes need to be
% written explicitly. In contrast, our region type inference that
% eliminates any such need.
